---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Source+Sans+3:ital,wght@0,200..900;1,200..900&display=swap');

body {
  background-color: #F7F6E5;
  font-family: 'Source Sans 3', sans-serif;
}

h2 {
  color: #DA4848;
  border-bottom: 2px solid #DA4848;
  font-weight: 700;
}

h3 {
  color: #76D2DB;
  border-bottom: 2px solid #76D2DB;
  font-weight: 550;
}

p {
  font-weight: 400;
}
```

## Analysis of My Digital Note-Taking Behaviour

Over a two-week period, I logged every study session where I used my iPad for note-taking. This report visualizes my study habits and quantifies the amount of physical paper I've saved.

```{r}
# Import the data from csv
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vShO4SMxN2LjWsJAfacWNI7Vdl-RlRIwCWndjqlhtVelZEmhYK_uQ4uKDX8b1qQipxOqmu5VHuakHBH/pub?gid=1368522283&single=true&output=csv")

# Rename columns to improve readability
latest_data <- logged_data %>%
  rename(timestamp = 1,
         course = 2,
         content_type = 3,
         pages = 4,
         density = 5,
         duration_minutes = 6)

# How many sessions in the data
total_sessions <- nrow(latest_data)

# What's the average ink density
avg_density <- mean(latest_data$density) %>% round(digits = 2)

# How many papers are saved in theory
total_pages <- sum(latest_data$pages)
```

So far, by going paperless for my studies with **`r total_sessions`** sessions, I have saved a total of **`r total_pages`** pages of paper!
The average "ink density" of my notes is **`r avg_density`** on a scale of 1 to 5. This shows that my notes are typically quite dense, leaning more towards text and equations than sparse diagrams.

## Workload & Style Breakdown

The charts below show which courses I'm working on most frequently and the nature of that work. We can see a breakdown of activities (notes, assignments) and the typical "ink density" of the notes for each subject.

```{r}
# Type of content in each course
latest_data %>%
  ggplot() +
  geom_bar(aes(x = course, fill = content_type)) +
  labs(title = "What kind of work am I doing in each course?",
       subtitle = "Breakdown of study sessions by content type across courses",
       caption = "Data collected over 14 days of iPad note-taking",
       x = "Course",
       y = "Number of Study Sessions",
       fill = "Content Type")
```
```{r}
# Which course is more ink density
latest_data %>%
  ggplot() + 
  geom_bar(aes(x = course, fill = as.factor(density))) + # convert a numerical variable into a factor to stop the warning
  labs(title = "Which course is more ink-heavy?",
       subtitle = "Breakdown of ink density across courses",
       caption = "Data collected over 14 days of iPad note-taking",
       x = "Course",
       y = "Number of Study Sessions",
       fill = "Ink Density\n1 - Mostly Spaces\n5 - Wall of Text")
```
